\documentclass{resume}
\RequirePackage{resume}

\begin{document}
	\begin{center}
		\name{Linxuan He}
		178-1211-0260 | hlx95108@gmail.com\\
		https://github.com/h9tyf\\
	\end{center}

	\section{Education}
	\datedsubsection{{\bfseries Beihang University} - School of Computing Science and Engineering - 
Undergraduate}{2018.09 - 2022.07}
c	\datedsubsection{{\bfseries GPA} : 3.61/4.00}{}
	\datedsubsection{{\bfseries Related Courses} : 
	Data Structure(93), Computer Organization(91),  
	Operating System(89), Compilation Technology(82),  
	Object-oriented Design and Construction(97), 
	Intelligent Computing Architecture(94), 
	Data Mining(90), 
	Ruby Program Design(96), 
	Swift Program Design(100).}{}


	\section{Professional Skills}
		\datedsubsection{{\bfseries Skills}: Python, Java, SQL, C, C++, C\#, Swift, Ruby, 
		HTML, MATLAB, Lingo}{}
		\begin{itemize}
		    \item Familiar with Python, Java, C/C++. Multiple projects were done with these languages.
		    \item C\#, Swift, Ruby: I have done related projects and have limited understanding.
		    \item About other languages, such as HTML, I only know a little when needed.
		\end{itemize}

	\section{Projects}
	The following projects can be found in my GitHub personal homepage.
	\datedsubsection{{\bfseries Elevator Tester} - Java. To evaluation my homework of object-oriented multithread unit, I together with a classmate finished this project.
	It mainly contains two parts: running Java code and getting output, evaluation for output. I am responsible for second part.}{}
	
	
	\datedsubsection{{\bfseries E-shop} - Ruby, HTML. 	A simple E-commerce system. It is implemented using Ruby on Rails framework, 
	and available for users to sell and buy.
	This has been deployed on Heroku, and its address is https://sleepy-plains-42331.herokuapp.com/.}{}

	
	\datedsubsection{{\bfseries CUMCM-2020-ProblemC} - Python. This project is the work of our team participating in CUMCM2020. 
	We built a risk assessment model by analysing corporate tax, invoice, and other 
	information. Finally we use this model to evaluate financial indicator information of these small to medium enterprises. We won the first prize in Beijing in this competition.}{}
	
	
	\datedsubsection{{\bfseries Compiler} - C++. 	A simple compiler written in C++, which uses automata to perform lexical analysis, 
	uses recursive descent parser to perform parsing, 
	and can realize the compilation of C-like syntax program to MIPS code.}{}

	
	\datedsubsection{{\bfseries Serverless Load Prediction} - Python. This project is Written in DataFountain's "Big Data SERVERLESS Workload Forecast" competition.
   It performs feature extraction and processing of data, and uses the LightGBM framework to predict workloads, so that the serverless software architecture can adjust elastic resources according to workloads. 
    Our ranking in this competition is 42/364.}{}
	
	
	\datedsubsection{{\bfseries Audio Recognition} - Python. Fourier transform is used to process audio. Then we divide the dataset, build the CNN network for training and recognize the new audio.
	Our model can identify the type of instrument in a piece of music with an accuracy of about 90\%.}{}
	
	
	\datedsubsection{{\bfseries Simple Supermarket Management System} - C\#. A simple supermarket management and shopping system. It implements the administrator's management of commodities, the viewing function of consumption records, and the customer's shopping settlement function. At the same time, a graphical interface is designed.}{}
	

	\section{Internship}
	I participate in the development of the platform for the submission and defense of the college's graduation design. 
	This project utilizes AWS PaaS paltform to achieve most functions, and I am responsible for using interface programming to realize new functions 
	when existing functions cannot meet demand. 
	For example, when forwarding the files submitted by students to the corresponding teachers, the platform cannot realize automatic forwarding. I achieved this function by java operations on the database and platform-related interfaces. 
	The platform is currently ready for final testing and is expected to be put into use this year.
	Starting this year, graduates of our college will use this platform to submit the weekly graduation design report and prepare for the defense.

\end{document}